Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-30 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
moved things to SI

  %MRS: combined the ``general'' material about models here.  
  We show that both stochastic models reasonably reproduce the MSDs
  calculated from MD simulations. However, qualitative differences
  between MD and Markov state dependent model-generated trajectories
  may in some cases limit their usefulness. With these parameterized
  stochastic models, we demonstrate how one can estimate flux of a
  solute across a macroscopic-length pore and, based on those
  quantities, the membrane's selectivity towards each solute. This
  work therefore helps to connect microscopic, chemically-dependent
  solute motions that do not follow simple diffusive behavior with
  long time-scale behavior, in an approach generalizable to many types
  of molecular systems with complex dynamics.

@@

  %MRS: agreed.
  % BJCA: Would it make more sense to have the first paragraph less
  % applications-focused and more centered around a need for our new methods?
  % Something like ..

There is a large disparity between the time scales accessible to
atomistic molecular dynamics (MD) simulations and experiment. The
dynamics of molecules over nanoseconds of simulation may tell a very
different story than that inferred by bulk measurements on the time
scale of seconds. Understanding complex dynamical behavior on short
timescales and connecting them with much longer timescales can provide
fundamental insight which can be used for atomic level design of
materials. In this work, we pursue this connection applied to highly
selective aqueous filtration membranes and demonstrate how one can
gain chemical intuition which serves both theoretical and experimental
researchers.

  Highly selective separations membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
  the materials industry, there is a strong interest in creating breathable
  fabrics which selectively allow passage of water
  vapor.~\cite{mondloch_destruction_2015}

  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
  % and its complex pores.
  %MRS: yes.  QI not relevant
  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate
  solute-specific separation membranes using the available chemical space of
  LLC monomers
  %BJCA added rest of sentence:
  by allowing us to understand their macroscopic behavior based on microscopic, chemically-dependent solute motions.
  To date, only a limited subset of LLC monomers have been
  studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

@@

  %BJCA: maybe this paragraph can be cut down?
  %MRS: provides context, so OK?
  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

  Using a bottom-up modeling approach, it may be possible to parameterize single
  particle behavior by extracting particle trajectories from MD simulations and
  studying the properties that have the greatest influence on solute dynamics.
  With this information, one can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. 
  %Fortunately,
  There is an abundance of information encoded in
  the complex solute trajectories. One can incorporate fluctuations and 
  time-dependent correlations in solute position into transport models, 
  as well as the length of time solutes are trapped. It is possible to add further
  detail by integrating this time series analysis with existing knowledge of the
  primary trapping mechanisms as well as the solute's changing chemical environment
  within the heterogeneous membrane.

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations. 
  %MRS: moved from below
  Where sufficiently close to observed data, these fitted models
  provide a way to propagate information about solute trajectories gathered 
  at the microsecond time scale to realistic experimental time scales.

  % BJCA: resurrected this paragraph
  % MRS: seems OK.
  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this on the simulation 
  time scales of this study.~\cite{klages_anomalous_2008}
  % BJCA: removing less technical version of above
%  The first model that we develop in this work allows us to characterize the 
%  hopping and trapping behavior displayed by solutes in our MD simulations. This 
%  type of non-Brownian dynamical behavior results in subdiffusive transport which
%  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%MRS: more concise better.
%BJCA: I could replace above with this, but I think I like the above better. It's more concise.
%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

%  We treated our system as an FBM process subordinate to a CTRW, or
%  subordinated FBM (sFBM) for short. 
  We fit sFBM models in two ways: First, we parameterize solute motion using
  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
  Second, we use a two-state approach by extracting two sets of model parameters
  calculated based on a solute's radial distance from the closest pore center. 
  This allows us to include the different dynamical behavior of solutes previously
  observed within the pore region versus within the monomer tails.

  % BJCA: Is this paragraph needed? 
  %MRS: the first sentence is key to the paper thesis and deserves to be emphasized, but I moved it up.
  %MRS: rest is somewhat redundant.
  %They can also confirm the importance of assumed solute-membrane interactions 
  %used to define the model's functional form, and
  %suggest missing components. They can help researchers formulate hypotheses to
  %explain why a certain set of parameters is characteristic to a specific
  %solute.

@@

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. It is also possible that solute dynamics will become diffusive on
  long simulation timescales. Therefore, the transition from subdiffusion to regular
  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD curves. 
  We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
  %MRS: good call.
  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

  One can measure MSD in two ways. The ensemble averaged MSD measures 
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the ensemble averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory.

  The time averaged and ensemble averaged MSDs will give identical results 
  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
  law distribution of trapping times leads to weak ergodicity breaking.
  In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
  power law trapping behavior, the time between hops diverges so there is no 
  characteristic measurement time scale of solute motion. In fact, as measurement 
  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
  aging, because trajectories with trapping times on the order of the measurement 
  time get incorporated into the calculation.~\cite{bel_weak_2005}

  We chose to use just the time-averaged MSD to compare MD trajectories with
  modeled trajectories, because, compared to the ensemble average, it is a more
  statistically robust measure of the average distance a solute travels over
  time. The ensemble MSD of only 24 solute trajectories would have much higher
  uncertainties.

@@

  %BJCA: I could get rid of this table and define them in text. 
  %MRS: eh, tables are a clear way to communicated data, so OK. 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  We find the data suggests that solute motion in this system can be
  well-modeled by subordinated fractional Brownian motion. In
  Figure~\ref{fig:solute_trajectories}, we plotted representative trajectories
  for each solute. They are characterized by intermittent hops between periods
  of entrapment. The near-Gaussian distribution of jump lengths and power law
  distribution of dwell times are both characteristic of CTRWs
  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}).  The
  apparent anti-correlation between hops suggests a fractional diffusion
  process is subordinate to the CTRW. Of the different models, a process
  subordinated by FBM or FLM is best supported by the data because the
  analytical correlation structures of hop lengths are close to those observed
  in our simulations (Figure~\ref{fig:hop_acf}). Fractional motion is common
  in crowded viscoelastic environments where motion is highly influenced by
  the movement of surrounding components, such as monomer tails in our
  case.~\cite{ernst_fractional_2012}

@@

  %BJCA: maybe this to supporting?
  %MRS: yeah, I think so. 
  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
  }\label{fig:anticorrelated_hops}
  \end{figure}

  We modeled the distributions of hop lengths in two ways. First, we assumed
  the distribution to be Gaussian since it is possible to exactly simulate
  realizations of fractional Brownian motion. Second, we fit the distributions
  to L\'evy stable distributions since it is more general than the Gaussian
  distribution. We plotted the MLE fits of both on top of urea's hop length
  distribution in Figure~\ref{fig:hop_distribution_comparison}. The L\'evy
  distribution does a better job capturing the somewhat heavy tails and high
  density near 0 of the hop length distribution. However, since there are no
  known exact simulation techniques for generating realizations of fractional
  L\'evy motion, this more general fit may not be worthwhile. In fact, we
  typically observe very little difference between model predictions
  parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).

  We also modeled the distribution of dwell times in two ways. First, we
  assumed pure power law behavior since it is consistent with most theoretical
  descriptions of CTRWs. The data fits well to this model at short dwell times
  but the density of long dwell times is over-estimated. In our second
  approach, we truncate the power law distribution with an exponential cut-off,
  lowering the probability of extremely long dwell times. We demonstrate this
  effect in the inset to Figure~\ref{fig:powerlaw}, where the density of the
  truncated power law drops below that of the pure power law and tends towards
  0 near a dwell time of 250 ns.

@@

>>>>

  We show that both stochastic models reasonably reproduce the MSDs calculated 
  from MD simulations. However, qualitative differences between MD and Markov 
  state dependent model-generated trajectories may in some cases limit their 
  usefulness. With these parameterized stochastic models, we demonstrate how 
  one can estimate flux of a solute across a macroscopic-length pore and, based
  on those quantities, the membrane's selectivity towards each solute. This
  work therefore helps to connect microscopic, chemically-dependent solute 
  motions that do not follow simple diffusive behavior with long time-scale 
  behavior, in an approach generalizable to many types of molecular systems 
  with complex dynamics.

@@

  There is a large disparity between the time scales accessible to atomistic 
  molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
  over nanoseconds of simulation may tell a very different story than that 
  inferred by bulk measurements on the time-scale of seconds. Understanding 
  complex dynamical behavior on short time-scales and connecting them with much
  longer time-scales can provide fundamental insight which can be used for 
  atomic level design of materials. In this work, we pursue this connection 
  applied to highly selective aqueous filtration membranes and demonstrate how
  one can gain chemical intuition which serves both theoretical and experimental
  researchers.

  Highly selective separations membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} 
  %BJCB: could cut this last sentence. It's kind of awkward  
  In the materials industry, there is a strong interest in creating breathable
  fabrics which selectively allow passage of water
  vapor.~\cite{mondloch_destruction_2015}

  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
  % and its complex pores.
  %MRS: yes.  QI not relevant
%  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
%  can be cross-linked into mechanically strong and highly selective nanoporous
%  membranes.~\cite{gin_polymerized_2008} They may provide a promising
%  alternative to conventional membrane separation techniques by being selective
%  based not only on solute size and charge, but on solute chemical
%  functionality as well.~\cite{dischinger_application_2017} One can tune the
%  functionality of LLC monomers in order to enhance or weaken specific
%  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
%  morphologies of LLC membranes are being actively developed. The inverted
%  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
%  pores on the order of 1 nm in size. A perfectly synthesized
%  H\textsubscript{II} phase has an ideal geometry for high throughput
%  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
%  a large scale as required for high permeability has shown limited
%  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
%  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
%  complex pores of the H\textsubscript{II} phase but its geometry consists of a
%  tortuous network of 3D interconnected pores which do not require
%  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
%  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
%  H\textsubscript{II} phase, it is considerably easier to produce 
%  at scale.~\cite{hatakeyama_nanoporous_2010}

  %BJCB: removed discussion of Q1 from above paragraph
  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017}

  % BJCB: split into two paragraphs  
  In this work, we study the inverted hexagonal, H\textsubscript{II}, LLC phase. 
  The H\textsubscript{II} phase has densely packed, uniform-sized pores on the 
  order of 1 nm in size. A perfectly aligned H\textsubscript{II} phase has 
  an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}
  %BJCB: could add a sentence saying that in pracftice, alignment is hard. Not sure if worth acknowledging for this paper.

  Molecular modeling may make it possible to efficiently evaluate solute-specific
  separation membranes using the available chemical space of LLC monomers by 
  allowing researchers to understand their macroscopic behavior based on 
  microscopic, chemically-dependent solute motions. To date, only a limited 
  subset of H\textsubscript{II} phase-forming LLC monomers have been studied
  experimentally in membrane applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

@@

  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

  Using a bottom-up modeling approach, it may be possible to parameterize single
  particle behavior by extracting particle trajectories from MD simulations and
  studying the properties that have the greatest influence on solute dynamics.
  With this information, one can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. There is an abundance of information encoded in
  the complex solute trajectories. One can incorporate fluctuations and 
  time-dependent correlations in solute position into transport models, 
  as well as the length of time solutes are trapped. It is possible to add further
  detail by integrating this time series analysis with existing knowledge of the
  primary trapping mechanisms as well as the solute's changing chemical environment
  within the heterogeneous membrane.

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations. Where sufficiently close to observed data,
  these fitted models provide a way to propagate information about solute 
  trajectories gathered at the microsecond time scale to realistic experimental 
  time scales.

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} 
  The tools introduced by fractional calculus are instrumental to this 
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the normally
  linear diffusion equation to fractional derivative orders, providing descriptions
  of a much more diverse set of behavior, including subdiffusion, a type of 
  anomalous diffusion exhibited by solutes on the simulation time scales of this
  study.~\cite{klages_anomalous_2008}

  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

  We fit sFBM models in two ways: First, we parameterize solute motion using
  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
  Second, we use a two-state approach by extracting two sets of model parameters
  calculated based on a solute's radial distance from the closest pore center. 
  This allows us to include the different dynamical behavior of solutes previously
  observed within the pore region versus within the monomer tails.

@@

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. It is also possible that solute dynamics will become diffusive on
  long simulation timescales. Therefore, the transition from subdiffusion to regular
  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD
  curves. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions as described in subsequent sections.

  % BJCB: condensed commented out section that follows into this paragraph
  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories. We chose to calculate the time-averaged MSD from 
  our MD simulations and stochastic models which measures all observed displacements
  over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory. In some situations, it may make
  more sense to use the ensemble MSD. We present further discussion of this
  choice in Section~\ref{S-section:msd} of the Supporting Information.

  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
  % MRS: good call.

%  In this study, we primarily use the MSD as a tool for characterizing the average
%  dynamic behavior of solute trajectories. Rather than using them to calculate 
%  diffusion constants or to relate our simulations to experimental measurements, we
%  compare MSDs calculated from MD simulations to those generated from our models 
%  in order to validate those models. Therefore, it is only important that we use a
%  consistent definition for calculating the MSD between modeled trajectories and
%  directly observed MD trajectories.
%
%  One can measure MSD in two ways. The ensemble averaged MSD measures 
%  displacements with respect to a particle's initial position:
%  \begin{equation}
%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation}
%  Fits to the ensemble averaged MSD will always reproduce the form of 
%  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
%  displacements over time lag $\tau$: 
%  \begin{equation}
%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
%  \label{eqn:tamsd}
%  \end{equation}
%  where T is the length of the trajectory. 
%  
%  The time averaged and ensemble averaged MSDs will give identical results 
%  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
%  law distribution of trapping times leads to weak ergodicity breaking.
%  In this case, the time-averaged MSD is linear while the ensemble averaged
%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
%  power law trapping behavior, the time between hops diverges so there is no 
%  characteristic measurement time scale of solute motion. In fact, as measurement 
%  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
%  aging, because trajectories with trapping times on the order of the measurement 
%  time get incorporated into the calculation.~\cite{bel_weak_2005}
%  
%  We chose to use just the time-averaged MSD to compare MD trajectories with
%  modeled trajectories, because, compared to the ensemble average, it is a more
%  statistically robust measure of the average distance a solute travels over
%  time. The ensemble MSD of only 24 solute trajectories would have much higher
%  uncertainties.

@@

  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  We find the data suggests that solute motion in this system can be
  well-modeled by subordinated fractional Brownian motion. In
  Figure~\ref{fig:solute_trajectories}, we plotted representative trajectories
  for each solute. They are characterized by intermittent hops between periods
  of entrapment. The near-Gaussian distribution of jump lengths and power law
  distribution of dwell times are both characteristic of CTRWs
  (See Figures~\ref{S-fig:hop_distribution_comparison} and~\ref{S-fig:powerlaw}
  of the Supporting Information). 
  %The apparent
  Anti-correlation between hops suggests a fractional diffusion process is 
  subordinate to the CTRW. Of the different models, a process subordinated by 
  FBM or FLM is best supported by the data because the analytical correlation 
  structures of hop lengths are close to those observed in our simulations 
  (See Figure~\ref{S-fig:hop_acf} of the Supporting Information). Fractional 
  motion is common in crowded viscoelastic environments where motion is highly
  influenced by the movement of surrounding components, such as monomer tails 
  in our case.~\cite{ernst_fractional_2012}

@@

%  %BJCA: maybe this to supporting?
%  %MRS: yeah, I think so. 
%  \begin{figure}
%  \centering
%  % Next 3: /figures/sfbm_distributions
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
%  \caption{}\label{fig:hop_distribution_comparison}
%  \end{subfigure}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
%  \caption{}\label{fig:powerlaw}
%  \end{subfigure}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
%  \caption{}\label{fig:hop_acf}
%  \end{subfigure}
%  \caption{Using urea as an example, (a) the distribution of hop lengths can be
%	  fit by a Gaussian in addition to a more general L\'evy stable
%	  distribution, though the L\'evy stable distribution does a better job of
%	  capturing the heavier tails and increased density near 0. We explore
%	  models fit to both distributions, as Gaussian hops are more convenient
%	  to model. (b) The distribution of dwell times is fit well by a power
%	  law but it over-estimates the probability density at long dwell
%	  times. A power law truncated with an exponential cut-off better
%	  describes the probability of long dwell times in our simulations. (c)
%	  The hops are negatively correlated to their previous hop. In
%	  combination, (a) -- (c) support modeling solutes as either
%	  subordinated fractional Brownian or L\'evy motion. All other solutes
%	  show similar distributions and autocorrelation functions (see
%	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
%  }\label{fig:anticorrelated_hops}
%  \end{figure}

  We modeled the distributions of hop lengths in two ways. First, we assumed
  the distribution to be Gaussian since it is possible to exactly simulate
  realizations of fractional Brownian motion. Second, we fit the distributions
  to L\'evy stable distributions since it is more general than the Gaussian
  distribution. We plotted the MLE fits of both on top of urea's hop length
  distribution in Figure~\ref{S-fig:hop_distribution_comparison} of the
  Supporting Information. The L\'evy distribution does a better job capturing
  the somewhat heavy tails and high density near 0 of the hop length distribution. 
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, this more general fit may not be 
  worthwhile. In fact, we typically observe very little difference between model
  predictions parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).

  We also modeled the distribution of dwell times in two ways. First, we
  assumed pure power law behavior since it is consistent with most theoretical
  descriptions of CTRWs. The data fits well to this model at short dwell times
  but the density of long dwell times is over-estimated. In our second
  approach, we truncate the power law distribution with an exponential cut-off,
  lowering the probability of extremely long dwell times. 
  %We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where 
  On long time scales, the density of the truncated power law drops below that
  of the pure power law and tends towards 0 near a dwell time of 250 ns.

@@

  % BJCB: I could summarize the four following paragraphs in terms of key
  % takeaways, like you suggested with the AD model above.
